### 2020-12-02 README.Rmd
updating readme file
updating licenses

> Rodriguez-Machado, S., Rodríguez-Cabrera, T.M., and Chakrabarty, P. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book <https://doi.org/{DOI-to-paper}>

@@

> Rodriguez-Machado, S., Rodríguez-Cabrera, T.M., and Chakrabarty, P. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations

>>>>

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book <https://doi.org/{DOI-to-paper}>

@@

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder: templates](/analysis/templates): Style of citations and reference list
